Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-03-26 supplementary_information/si.Rnw
fix fig

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s
library(broom) # for tidy summaries

@@

# bind the three data frames, set factor order for type so pretty plot
three_studies = bind_rows(first_panel,second_panel,third_panel) %>% 
  dplyr::mutate(
    type = factor(type, levels = c('Participant responses', 'GCM', 'MGL'))
  )

# plot this, x is baseline, y is posttest.
# colour AND shape are lexical typicality.
# split panels across raw data / gcm / mgl.
# add loess smooths.
p1 = ggplot(three_studies, aes(x = baseline, y = posttest, colour = co_player_lexical_typicality, shape = co_player_lexical_typicality, linetype = co_player_lexical_typicality)) +
  guides(size = F) +
  geom_point() +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type, ncol = 2) +
  scale_shape_discrete(name="Lexical\ntypicality") +
  # scale_colour_discrete(name="Lexical\ntypicality") +
  xlab('verb baseline regularization') +
  ylab('verb ESP regularization') +
  guides(linetype = F) +
  theme_bw() +
  scale_colour_brewer(palette = 'Set2', name="Lexical\ntypicality")

>>>>

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s
library(broom) # for tidy summaries
library(ggthemes) # for colourblind scale

@@

# bind the three data frames, set factor order for type so pretty plot
three_studies = bind_rows(first_panel,second_panel,third_panel) %>% 
  dplyr::mutate(
    type = factor(type, levels = c('Participant responses', 'GCM', 'MGL')),
    linetype = case_when(
      co_player_lexical_typicality == 'typical' ~ 'solid',
      co_player_lexical_typicality == 'random' ~ 'dotdash',
      co_player_lexical_typicality == 'reversed' ~ 'twodash'
    )
  )

# plot this, x is baseline, y is posttest.
# colour AND shape are lexical typicality.
# split panels across raw data / gcm / mgl.
# add loess smooths.
p1 = ggplot(three_studies, aes(x = baseline, y = posttest, colour = co_player_lexical_typicality, shape = co_player_lexical_typicality, linetype = linetype)) +
  guides(size = F) +
  geom_point(alpha = .25) +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type, ncol = 2) +
  scale_shape_discrete(name="Lexical\ntypicality", solid = FALSE) +
  # scale_colour_discrete(name="Lexical\ntypicality") +
  xlab('verb baseline regularization') +
  ylab('verb ESP regularization') +
  guides(linetype = F) +
  theme_bw() +
  scale_colour_colorblind() +
  scale_linetype_identity()
